Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-31 paper-arxiv-v1/HH4b.tex
Added v2 of paper in repo

\author{Katharina Behr, Daniela Bortoletto, James Frost,
  Nathan P. Hartland, Cigdem Issever and Juan Rojo}

@@

\abstract{
  The measurement of Higgs pair production will be a cornerstone of
  the LHC program in the coming years.
  %
  Double Higgs production provides a crucial window upon the mechanism of electroweak
  symmetry breaking and has a unique sensitivity
  to the Higgs trilinear coupling.
  %
  We study the feasibility of a measurement of
  Higgs pair production in the
  $b\bar{b}b\bar{b}$ final state at the LHC.
  %
  Our analysis is based on a combination of traditional cut-based
  methods with state-of-the-art
  multivariate techniques.
  %
  We account for all relevant
  backgrounds, including the contributions from light and charm
  jet mis-identification, which are ultimately comparable in size 
  to the irreducible $4b$ QCD background.
  %
  We demonstrate the robustness of our analysis strategy in
  a high pile-up environment.
  %
  For an integrated luminosity of $\mathcal{L}=3000~(300)$ fb$^{-1}$,
  a signal significance of  $S/\sqrt{B}\simeq 7.2~(2.3)$ is obtained,
  indicating
  that the $b\bar{b}b\bar{b}$ final state
alone could allow for the discovery of double Higgs production
at the High Luminosity LHC.
%
We also find that, provided light and charm
jet mis-identification can be reduced, observation of
Higgs pairs in the $b\bar{b}b\bar{b}$ final state could
be within reach already at Run II.
}

>>>>

\author{Janna Katharina Behr, Daniela Bortoletto, James A. Frost,
  Nathan P. Hartland, Cigdem Issever and Juan Rojo}

@@

\abstract{
  The measurement of Higgs pair production will be a cornerstone of
  the LHC program in the coming years.
  %
  Double Higgs production provides a crucial window upon the mechanism of electroweak
  symmetry breaking and has a unique sensitivity
  to the Higgs trilinear coupling.
  %
  We study the feasibility of a measurement of
  Higgs pair production in the
  $b\bar{b}b\bar{b}$ final state at the LHC.
  %
  Our analysis is based on a combination of traditional cut-based
  methods with state-of-the-art
  multivariate techniques.
  %
  We account for all relevant
  backgrounds, including the contributions from light and charm
  jet mis-identification, which are ultimately comparable in size 
  to the irreducible $4b$ QCD background.
  %
  We demonstrate the robustness of our analysis strategy in
  a high pileup environment.
  %
  For an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$,
  a signal significance of  $S/\sqrt{B}\simeq 3$ is obtained,
  indicating
  that the $b\bar{b}b\bar{b}$ final state
alone could allow for the observation of double Higgs production
at the High Luminosity LHC.
}
